Data-Driven Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles\\ \thanks{This work was partially supported by AutonomouStuff (https://autonomoustuff.com/)}

### 2022-10-06 paperIEEE-ROSE2022.tex
Modified the contrb. statements in the abstract

  In this paper, we present data-driven hardware-in-the-loop (HIL) plant models of different subsystems of a self-driving vehicle. Despite numerous concerns, the automotive industry is still investing remarkable resources for producing self-driving vehicles to be available in the market. Among numerous challenges in the development process of such vehicles are the validation and testing process of various subsystems. Here we provide data-driven models of different subsystems so that automotive industries can validate and test autonomous vehicles without the need of a physical vehicle, which indeed reduces the considerable amount of cost for automotive industries. The vehicle subsystems considered in this work include steering, acceleration, brake, shift, speed, and speed control subsystems. Each of these subsystems is either a multi-input single output or single-input single output system. A Lexus RX450H self-driving vehicle is employed to collect raw data (inputs and outputs data for different subsystems) offline. We used the deep learning toolbox available in the commercial software package, MATLAB/SIMULINK, for modeling each of these systems. Therefore, the results of such modeling could be used for validating and testing without the need for a physical self-driving vehicle. As such, the proposed modeling results could be useful for reducing cost of vehicles' development process since a physical vehicle is not required for validation and testing. However, the performance of the steering, acceleration, and brake subsystems demonstrated for conciseness purpose. The contribution of this project is twofold. The first part is that we were able to take real time raw data collected from a Lexus RX450H vehicle and use it to develop machine learning models to represent the vehicle subsystems. The second portion of our contribution is that we took the models that we created and tested them using Hardware-in-the-Loop.

>>>>

  In this paper, we present data-driven hardware-in-the-loop (HIL) plant models of different subsystems of a self-driving vehicle. Despite numerous concerns, the automotive industry is still investing remarkable resources for producing self-driving vehicles to be available in the market. Among numerous challenges in the development process of such vehicles are the validation and testing process of various subsystems. Here we provide data-driven models of different subsystems so that automotive industries can validate and test autonomous vehicles without the need of a physical vehicle, which indeed reduces the considerable amount of cost for automotive industries. The vehicle subsystems considered in this work include steering, acceleration, brake, shift, speed, and speed control subsystems. Each of these subsystems is either a multi-input single output or single-input single output system. A Lexus RX450H self-driving vehicle is employed to collect raw data (inputs and outputs data for different subsystems) offline. We used the deep learning toolbox available in the commercial software package, MATLAB/SIMULINK, for modeling each of these systems. The contribution of this paper is twofold. First, collecting real time raw data from a physical Lexus RX450H vehicle and use it to develop machine learning models to represent the vehicle subsystems. Second, subsystem models created using machine learning tools for the Lexus vehicle are tested using Hardware-in-the-Loop. Therefore, the results of such modeling could be used for validating and testing without the need for a physical self-driving vehicle. The proposed modeling results could be useful for reducing cost of vehicles' development process since a physical vehicle is not required for validation and testing. However, the performance of the steering, acceleration, and brake subsystems demonstrated for conciseness purpose. .
